Dynein project log

### 2016-09-23 thesis_stuff/thesis_stuff.tex
Add a bit more to thesis_stuff.tex.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & & &\\ \hline
    $L_t$ &  & & & &\\ \hline
    $R_b$ &  & & & &\\ \hline
    $R_m$ &  & & & &\\ \hline
    $R_t$ &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & & & & &\\ \hline
    $\theta_{m}^{Post}$ & & & & &\\ \hline
    $\theta_{b}$ & 56 & & & &\\ \hline
    $\theta_{t}$ & 0 & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$? review & & & &\\ \hline
    $k_b$ & $1000 s^{-1,b}$? review & & & &\\ \hline
  \end{tabular}
\end{center}

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & & &\\ \hline
    $L_t$ &  & & & &\\ \hline
    $R_b$ &  & & & &\\ \hline
    $R_m$ &  & & & &\\ \hline
    $R_t$ &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & & & 171$^{\circ}$ & &\\ \hline
    $\theta_{m}^{Post}$ & & & 137.5$^{\circ}$ & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
    \caption{Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}
